Conformance Checking Using Embeddings and it's Applicability in the Internet of Things

### 2021-12-20 paper.tex
Fixes

\begin{abstract}
	In the last decade, there has been growing interest, both scientific and non-scientific, in the field of process mining.
	While the main focus has been on business processes, the methods developed in the field of process mining are in no way limited to that area.
	One other area which lends itself to process mining is the growing Internet of Things.
	While there are many conceivable applications,  there has only been limited research interest in this synergy.
	The aim of this seminar paper is to recapitulate the findings of the focus paper \cite{PBWe20}, while also emphasizing the benefits and difficulties of applying the described methodology in the Internet of Things.
\end{abstract}

@@

One benefactor of this development has been the subfield of process science, which is concerned with the analysis of processes.
The combination of process science and data science gave rise to techniques generally grouped under the term process mining
%\footnote{Please note that due to the relatively young age of the field, the fact that it lies at the intersection of two different fields and the fact that there is a marketing interest for these topics the terminology is not always settled and different authors and/or groups may differ in usage. The terminology used here is oriented around the definitions in \cite{Aals16}, as it seems to be the most polished overview of the field at the moment.}.
Process mining is concerned with the automatic and algorithmic processing of event data. In its easiest form, an event is a piece of data, that consists of a timestamp, an identifier to group events belonging to the same execution, and a body containing further arbitrary values.
In most cases, there is also an identifier for the event type, with the purpose of identifying similar events in different executions of the process, e.g. to be able to group all "Send invoice" events as the same type.

>>>>

\begin{abstract}
	In the last decade, there has been growing interest, both scientific and non-scientific, in the field of process mining.
	While the main focus has been on business processes, the methods developed in the field of process mining are in no way limited to that area.
	One other area which lends itself to process mining is the growing Internet of Things.
	This synergy is interesting from the side of the Internet of Things, where a desire exists for greater analytical capacities regarding processes, 
	but it is also interesting from the side of process management, where a desire for new and different types of processes is growing.
	The aim of this seminar paper is to recapitulate the findings of the focus paper \cite{PBWe20}, while also emphasizing the benefits and difficulties of applying the described methodology in the Internet of Things.
\end{abstract}

@@

One benefactor of this development has been the subfield of process science, which is concerned with the analysis of processes.
The combination of process science and data science gave rise to techniques generally grouped under the term process mining
%\footnote{Please note that due to the relatively young age of the field, the fact that it lies at the intersection of two different fields and the fact that there is a marketing interest for these topics the terminology is not always settled and different authors and/or groups may differ in usage. The terminology used here is oriented around the definitions in \cite{Aals16}, as it seems to be the most polished overview of the field at the moment.}.
Process mining  \cite{Aals16} is concerned with the automatic and algorithmic processing of event data. In its easiest form, an event is a piece of data, that consists of a timestamp, an identifier to group events belonging to the same execution, and a body containing further arbitrary values.
In most cases, there is also an identifier for the event type, with the purpose of identifying similar events in different executions of the process, e.g. to be able to group all "Send invoice" events as the same type.
